Co-methylation

### 2015-05-06 Rmarkdown/comethylation.Rmd
Final touches

\citet{Breslow:1981ta} showed that under $A2$ neither the unconditional maximum likelihood estimator, $\widehat{\psi}_{U}$, nor the '0.5-adjusted' unconditional maximum likelihood estimator, $\widehat{\psi}_{0.5}$, converge to the true odds ratio. In contrast, both the Mantel-Haenszel estimator, $\widehat{\psi}_{MH}$, and the conditional maximum likelihood estimator, $\widehat{\psi}_{C}$, do converge to $\psi$, with $\widehat{\psi}_{MH}$ having the advantage of a simple closer form expression \citep{Breslow:1996uc}.

>>>>

\citet{Breslow:1981ta} showed that under $A2$ that the unconditional maximum likelihood estimator does not converge to the true odds ratio. In contrast, both the Mantel-Haenszel estimator and the conditional maximum likelihood estimator do converge to the true odds ratio, with the Mantel-Haenszel estimator having the advantage of a simple closed form expression \citep{Breslow:1996uc}.
